Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-12 paper.qmd
Updated MNIST model building

algo_obj_mnist <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_mnist, 
  nldr_data = tsne_mnist2, 
  num_x_bins = num_bins_x_mnist)

tsne_minst_scaled <- algo_obj_mnist$nldr_scaled
tr_from_to_df_mnist <- algo_obj_mnist$tr_from_to_df
df_bin_centroids_mnist <- algo_obj_mnist$df_bin_centroids
df_bin_mnist <- algo_obj_mnist$df_bin

@@

# tr_from_to_df_mnist <- tr_from_to_df_mnist |>
#   mutate(ID = row_number()) |>
#   filter(!(ID %in% c(1205, 1629, 1170)))

@@

hexID_mnist <- df_bin_centroids_mnist |>
  dplyr::filter(std_counts > 0) |>
  dplyr::pull(hexID)

>>>>

algo_obj_mnist <- fit_highd_model(
  highd_data = training_data_mnist, 
  nldr_data = tsne_mnist2, 
  bin1 = num_bins_x_mnist, 
  q = 0.1, 
  benchmark_highdens = 5)

tsne_minst_scaled <- algo_obj_mnist$nldr_obj$scaled_nldr
tr_from_to_df_mnist <- algo_obj_mnist$trimesh_data
df_bin_centroids_mnist <- algo_obj_mnist$model_2d
df_bin_mnist <- algo_obj_mnist$model_highd

@@

@@

hexID_mnist <- df_bin_centroids_mnist |>
  #dplyr::filter(std_counts > 0) |>
  dplyr::pull(hexID)
